### 2017-11-09 Graduate - Introduction to Analysis I/Assignment 7/7-Homework20171108.tex
add prob 3

\documentclass{article}%
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{amsfonts}%
\usepackage{amssymb}

@@

\item  Problem 10, Chapter 6
\item  Problem 13, Chapter 6
\item  Problem 16, Chapter 6

>>>>

\documentclass{article}%
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{amsfonts}%
\usepackage{amssymb}
\usepackage{hyperref}

@@

\item  Problem 10, Chapter 6
\item  Problem 13, Chapter 6

\smallskip
\textbf{Solution:}
\smallskip
First, we show that under the conditions of the Vitali Covering Lemma, $\mathcal{F}\setminus \bigcup\limits_{k=1}^n I_k $ is a Vitali covering of $E\setminus \bigcup\limits_{k=1}^n I_k$. In fact, if it is not true, then there $\exists x\in E\setminus\bigcup\limits_{k=1}^n I_k$ and $\epsilon > 0$, s.t. there does not exist an interval $I\in\mathcal{F}\setminus\bigcup\limits_{k=1}^n I_k$, s.t. $x\in I$, and $m(I) < \epsilon$. However, since $\mathcal{F}$ is a Vitali covering of $E$, then for $\epsilon_i = \frac{\epsilon}{2^i}, ~i = 1, 2, \cdots $, there exists $I_i'\in\mathcal{F} $, s.t. $x\in I_i' $ and $m(I_i') < \epsilon_i $. If there exists $i_0 $, s.t. $I_{i_0}\notin \{I_k\}_{k = 1}^{n} $, then $x\in I_{i_0} $ and $m(I_{i_0}) < \epsilon$, which makes a contradiction. Then $\{I_i'\} \in \{I_k\}_{k = 1}^{n}$, but it contradicts with $n < \infty$. Hence, our claim is proved.

Then we show that if $\{I_k\}_{k=1}^{n} $ is a finite sequence of closed intervals, then we can find a pairwise disjoint subsequence $\{I_{k_j}\}$ s.t. 
$$
m(\bigcup_{j = 1}^{m} I_{k_j}) \ge m(\bigcup_{k=1}^{n}I_k).
$$
The proof of this proposition can be seen at \href{http://www.personal.psu.edu/t20/papers/vitali-l2h/node5.html}{http://www.personal.psu.edu/t20/papers/vitali-l2h/node5.html}

Now we use these claims to construct a collection. Using Vitali Covering Lemma, for $\epsilon = \frac{3}{4}m(E)$, there exists a finite collection of disjoint intervals $\{I_k\}$, s.t. $m(E\setminus \bigcup I_k) < \epsilon$. Denote $A = \bigcup I_k $.

Since $\mathcal{F}\setminus A$ is a Vitali covering of $E\setminus I_k $, there is a finite set of intervals $J_k $, s.t. $J_k\subset E\setminus A $ (Otherwise just follow the proof of Vitali Covering Lemma on the textbook), and 
$$
m(E\setminus (A\cup\bigcup_{k=1}^m J_k)) < \frac{1}{12}m(E\setminus A).
$$
Then using claim 2, there is a pairwise disjoint subset $\{J_{k_i}\}$ s.t. 
$$
m(\bigcup J_{k_i}) \ge \frac{1}{3}m(\bigcup J_k).
$$
Then denote $B = \bigcup J_{k_i} $, and 
$$
m(E\setminus (A\cup B)) < \frac{2}{3}m(\bigcup J_k) +\frac{1}{12}m(E\setminus A) \le (\frac{2}{3}+\frac{1}{12})m(E\setminus A) = \frac{3}{4}m(E\setminus A).
$$
By constructing like above recursively, we can get a sequence of subsets $\{A_i\}$, s.t. 
$$
m(E\setminus \bigcup_{i=1}^n A_i) \le (\frac{3}{4})^n m(E).
$$
By countable addivity,
$$
m(E\setminus \bigcup_{i=1}^\infty A_i) = 0.
$$

\item  Problem 16, Chapter 6
